They're Clutching up! Team Momentum in Round-Based Esports

### 2022-08-14 presentation/presentation.qmd
replace paper/ with paper2/. move presentation, data, and scripts to dirs

@@

cod_theoretical_constant_p2 <- cod_theoretical_series_lengths2 |> 
  slice_max(theoretical_series_length, n = 1) |> 
  pull(p)

>>>>

```{r}
#| label: cod_streak_series
cod_streaks_res$series |> 
  arrange(n_rounds) |> 
  transmute(
    `# of rounds (i)` = n_rounds, 
    `P(i)` = scales::percent(prop_expected, accuracy = 0.1)
  ) |> 
  knitr::kable()

cod_streaks_res$series |> 
  select(
    n_rounds,
    prop_expected,
    prop_actual,
    n_actual
  ) |> 
  arrange(n_rounds) |> 
  gt::gt() |> 
  gt::cols_label(
    n_rounds = '# of rounds (i)', 
    prop_expected = 'P(i)',
    prop_actual = '%',
    n_actual = 'N'
  ) |> 
  gt::fmt_percent(
    decimals = 1,
    columns = c('prop_expected', 'prop_actual')
  ) |> 
  gt::cols_align(
    align = 'right',
    columns = c('prop_expected', 'prop_actual')
  ) |> 
  gt::tab_spanner(
    label = 'Observed',
    columns = c('prop_actual', 'n_actual')
  ) |> 
  gt::as_latex() |> 
  pluck(1)
```

@@

cod_theoretical_constant_p2 <- cod_theoretical_series_lengths2 |> 
  slice_max(theoretical_series_length, n = 1, with_ties = FALSE) |> 
  pull(p)
